\documentclass[11pt,a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage{helvet}
    \renewcommand{\familydefault}{\sfdefault}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.75in,right=0.75in,bottom=0.6in,top=0.6in]{geometry}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-34pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Federico González}}\\
    {\large \scshape {Full Stack Developer}}\\
	Montevideo, Uruguay | 03.federico.gonzalez@gmail.com | +59895152599\\
\end{center}

%==== Experience ====%
\header{Experience}
\vspace{0mm}

\textbf{ST Consultores} \hfill Montevideo, Uruguay\\
\textit{Full Stack Developer} \hfill Jun 2023 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep -1pt
	\item Developed and maintained full-stack applications using Java, JavaScript, TypeScript, React, Oracle and Postgres databases.
	\item Deployed and managed applications on JBoss and Tomcat servers.
	\item Collaborated with cross-functional teams to design, develop, and deploy new features.
	\item Contributed to the entire software development lifecycle, from requirements gathering, estimation, and design to implementation, testing, and deployment.
	\item Improved application performance and scalability by writing efficient code and optimized database queries.
	\item Integrated third-party APIs and services to enhance application functionality.
	\item Built REST APIs to facilitate smooth data flow between client and server, and to expose data for external system integrations.
	\item Designed manuals and documentation for end-users and developers.
\end{itemize}
\vspace{-1mm}
\textit{Tools: TypeScript, JavaScript, Java, React, Oracle, Postgres, JBoss, Tomcat, REST APIs, Git.}

\vspace{1.5mm}
\hrule
\vspace{1.5mm}

\textbf{KodaTek} \hfill Montevideo, Uruguay\\
\textit{Full Stack Developer} \hfill Dec 2021 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep -1pt
	\item Developed and maintained full-stack web applications for client projects, with strong focus on backend development.
	\item Built and maintained REST APIs using Node.js and Express to support business logic, integrations, and internal processes.
	\item Designed and optimized database structures, queries, and data flows using PostgreSQL.
	\item Developed responsive frontend interfaces using React, Next.js, JavaScript, and TypeScript.
	\item Built workflow automations using n8n to connect services, streamline operations, and reduce manual tasks.
	\item Integrated third-party services and external APIs to extend application functionality and support automation workflows.
	\item Participated in the full software development lifecycle, from requirements analysis and technical design to implementation, deployment, and support.
\end{itemize}
\vspace{-1mm}
\textit{Tools: TypeScript, Node.js, Express, React, Next.js, JavaScript, PostgreSQL, n8n, REST APIs, Git.}
\vspace{1.5mm}

%==== Education ====%
\header{Education}
\textbf{ORT University}\hfill Uruguay\\
BSc Systems Engineering \textit{In progress} \hfill Mar 2022 - Present\\
\vspace{1.5mm}





\header{Certifications}
\textbf{C2 EF Set English Certificate} \hfill EF SET\\
https://cert.efset.org/es/XiQmLL \hfill Mar 2026\\
\vspace*{1mm}
\textbf{Oracle Certified Associate Java Programmer (OCAJP) 1Z0-808 Course} \hfill Learn IT University\\
https://ude.my/UC-90514bcb-d4bc-48ba-873f-1712e5075ecb \hfill Jan 2024\\
\vspace*{1mm}

\ 
\end{document}
